Classify veg

### 2021-03-05 R/classify_species.Rmd
run script again, using freshly named file that is cleaned and filtered for classification

# read the cleaned data, labeled for train, test, 
cleaned_data <- readr::read_csv(here::here("analysis", "data", "derived_data", 
                                              "cleaned_spectra.csv"))
```

>>>>

# read the cleaned data, labeled for train, test, 
cleaned_data <- readr::read_csv(here::here("analysis", "data", "derived_data", 
                                              "cleaned_filtered_spectra.csv"))
```
